---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 150
)
```

# linkfunctions

<!-- badges: start -->
<!-- badges: end -->

The goal of `linkfunctions` is to provide a comprehensive and unified collection of link functions for statistical modelling.

`link` objects implemented in `linkfunctions` come with exact analytical formulas for both the first and second derivatives of link function and inverse link function.

## Installation

You can install the development version of `linkfunctions` from [GitHub](https://github.com/) with:

``` {r}
# install.packages("pak")
pak::pak("giovannitinervia9/linkfunctions")
library(linkfunctions)
```

## Core Features
Each link function in this package is an S3 object containing:

- `linkfun(theta)`: Map parameter $\theta$ to linear predictor $\eta$

- `linkinv(eta)`: Map linear predictor $\eta$ to parameter $\theta$

- `theta_eta(eta)`: First derivative $d\theta / d\eta$

- `theta2_eta2(eta)`: Second derivative $d^2\theta / d\eta^2$

- `eta_theta(theta)`: First derivative $d\eta / d\theta$

- `eta2_theta2(theta)`: Second derivative $d^2\eta / d\theta^2$.


## Visualizing Link Functions 
The package includes a convenient plot method to inspect the behavior of the link and its inverse.

```{r}
plot(logit_link())
```

## Advanced Parametric Links
`linkfunctions` implements some non-standard links. For example, the `softplus_link` is a smooth approximation of the ReLU function (common in Deep Learning), or `power_link` for Box-Cox transformations.

```{r}
plot(softplus_link(2))
```

## Handling Bounded Parameters
It is possible to easily model parameters constrained to arbitrary intervals (e.g., percentages 0-100, or physical limits) via the `bounded_link`.

```{r}
plot(bounded_link(lwr = -3, upr = 5))
```

## Available Link Functions

For parameters in $(0, 1)$:

- `logit_link()`
- `probit_link()`
- `cauchit_link()`
- `cloglog_link()`
- `loglog_link()`

For positive reals $(0, \infty)$:

- `log_link()`
- `sqrt_link()`
- `inverse_link()`
- `inverse_sq_link()`
- `softplus_link(a)`
- `power_link(lambda)`

For parameters in $(-1, 1)$:

- `rhobit_link()`

For bounded parameters:

- `lower_bounded_link(lwr)`
- `upper_bounded_link(upr)`
- `bounded_link(lwr, upr)`

For real numbers $(-\infty, \infty)$:

- `identity_link()`
